\chapter{Dataset} 

Introductory lines...

\section{Review}

\subsection{Pecan street}

The dataport by Pecan street collected high-resolution, appliance-level electricity use data from approximately 1,000 houses and apartments in the U.S. \cite{pecanstreet}. 

\section{Input data by FLEX-Operation model}

In order to accurately anticipate household's energy costs,
the FLEX-Operation model takes a set of variables into account,
and they can be divided into following 15 categories: 

\begin{itemize}
    \item behaviour profile,
    \item battery,
    \item behaviour, 
    \item boiler,
    \item building,
    \item energy price,
    \item heating element, 
    \item hot water tank,
    \item \gls{pv},
    \item region,
    \item space cooling technology,
    \item space heating tank,
    \item vehicle,
    \item energy price,
    \item region weather. 
\end{itemize}

Furthermore, the specific data required within each category is shown in table \ref{tab:dataset}. 

\begin{center}
    \tiny
    \begin{longtable}{ | p{.10\textwidth} | p{.80\textwidth} | }
        \hline 
        \multicolumn{1}{|c|}{\textbf{Category}} & \multicolumn{1}{c|}{\textbf{Data}} \\ 
        \hline 
        \endfirsthead

        \multicolumn{2}{l}
        {{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
        \hline \multicolumn{1}{|c|}{\textbf{Category}} &
        \multicolumn{1}{c|}{\textbf{Data}} \\  
        \endhead

        \multicolumn{2}{|r|}{{Continued on next page}} \\ 
        \hline
        \endfoot

        \endlastfoot
        
            Behaviour profile & id\_hour, people\_at\_home\_profile\_1, hot\_water\_demand\_profile\_1, appliance\_electricity\_demand\_profile\_1, vehicle\_at\_home\_profile\_1, vehicle\_distance\_profile\_1. \\
            \hline 
            Battery & ID\_Battery, capacity, capacity\_unit, charge\_efficiency, charge\_power\_max, charge\_power\_max\_unit, discharge\_efficiency, discharge\_power\_max, discharge\_power\_max\_unit. \\
            \hline 
            Behaviour & ID\_Behavior, id\_people\_at\_home\_profile, target\_temperature\_at\_home\_max, target\_temperature\_at\_home\_min, target\_temperature\_not\_at\_home\_max, target\_temperature\_not\_at\_home\_min, shading\_solar\_reduction\_rate, shading\_threshold\_temperature, temperature\_unit, id\_hot\_water\_demand\_profile, hot\_water\_demand\_annual, hot\_water\_demand\_unit, id\_appliance\_electricity\_demand\_profile, appliance\_electricity\_demand\_annual, appliance\_electricity\_demand\_unit, id\_vehicle\_at\_home\_profile, id\_vehicle\_distance\_profile. \\
            \hline 
            Boiler & ID\_Boiler, type, power\_max, power\_max\_unit, carnot\_efficiency\_factor. \\
            \hline 
            Building & ID\_Building, type, construction\_period\_start, construction\_period\_end, person\_num, Af, Hop, Htr\_w, Hve, CM\_factor, Am\_factor, internal\_gains, effective\_window\_area\_west\_east, effective\_window\_area\_south, effective\_window\_area\_north, grid\_power\_max, supply\_temperature. \\
            \hline
            Energy price & ID\_EnergyPrice, id\_electricity, id\_electricity\_feed\_in, id\_gases, price\_unit. \\
            \hline
            Heating element & ID\_HeatingElement, power, power\_unit, efficiency. \\
            \hline 
            Hot water tank & ID\_HotWaterTank, size, size\_unit, surface\_area, surface\_area\_unit, loss, loss\_unit, temperature\_start, temperature\_max, temperature\_min, temperature\_surrounding, temperature\_unit. \\
            \hline 
            \gls{pv} & ID\_PV, size, size\_unit. \\
            \hline
            Region & ID\_Region, code, year, norm\_outside\_temperature. \\
            \hline 
            Space cooling technology & ID\_SpaceCoolingTechnology, efficiency, power, power\_unit. \\
            \hline 
            Space heating tank & ID\_SpaceHeatingTank, size, size\_unit, surface\_area, surface\_area\_unit, loss, loss\_unit, temperature\_start, temperature\_max, temperature\_min, temperature\_surrounding, temperature\_unit. \\
            \hline 
            Vehicle & ID\_Vehicle, type, capacity, capacity\_unit, consumption\_rate, consumption\_rate\_unit, charge\_efficiency, charge\_power\_max, charge\_power\_max\_unit, discharge\_efficiency, discharge\_power\_max, discharge\_power\_max\_unit, charge\_bidirectional. \\
            \hline 
            Energy price & Region, year, id\_hour, electricity\_1, electricity\_2, electricity\_feed\_in\_1, gases\_1. \\
            \hline 
            Region weather & region, year, id\_hour, pv\_generation, pv\_generation\_unit, temperature, temperature\_unit, radiation\_south, radiation\_east, radiation\_west, radiation\_north, radiation\_unit. \\
            \hline 
        
        \caption{Input data required by FLEX-Operation}
        \label{tab:dataset}
    \end{longtable}
\end{center}
