\clearpage % Start a new page

\chapter{Privacy Policy}
\label{appendix:privacy}

This Privacy Policy outlines how University of Siegen and The Fraunhofer Institute for Systems and Innovation Research (ISI) collect, use, and protect data for research purposes.

\section*{Data Collection}

When you use our service, we collect data for research purposes. All data will be anonymous, meaning that we will not collect any personal information that can identify you. The data we collect may include, but is not limited to, information about your usage of the service, your location, and demographic information. 

\section*{Data Use}

We will use the data collected to conduct research and may publish papers based on the findings. The data will be used only for research purposes and will be safely taken care of by and only by all the parties involved in this research, which are University of Siegen and The Fraunhofer Institute for Systems and Innovation Research (ISI).

\section*{Data Retention}

Please note that once you have used our service, you cannot delete your data. This is because your data will become part of a larger pool of data that will be analysed anonymously. The data will be retained for as long as is necessary for research purposes.

\section*{Data Security}

We take appropriate measures to protect the data we collect from unauthorized access, use, or disclosure. We use industry-standard security protocols and techniques to safeguard the data from unauthorized access, use, or disclosure. All the parties involved in this research, which are University of Siegen and The Fraunhofer Institute for Systems and Innovation Research (ISI), will have access to the data.

\section*{Data Sharing}

We do not share the data we collect with third parties, except as required by law or with your explicit consent.

\section*{Changes to this Policy}

We reserve the right to modify this Privacy Policy at any time, so please review it frequently. If we make any changes to this Privacy Policy, we will post the revised version on our website.

\section*{Contact Us}

If you have any questions or concerns about this Privacy Policy or our data collection and processing practices, please contact us.